Cluster Detection from three-dimensional Lensing Mass Map

### 2021-01-09 doc/paper_ms_method_HSCY1/sparse_NFW_results.tex
update summary
typo correction in paper

The right panel of Figure \ref{fig_detoffsets} shows the average redshift of
true detections for each halo. The estimated redshifts are lower than the true
redshifts by about $0.03$ for halos in the low-redshift range ($z\leq
0.4$).  For halos at $0.4<z\leq 0.85$, the relative redshift bias is below
$0.5\%$.

With the intent to suppress false detections, we select peaks with values
greater than an ad-hoc threshold as candidates of galaxy clusters following
\citet{WL-massMap-clusDet-HSC-Miyazaki2018}.  The threshold is set to a few
times the standard deviation of the noise peaks. We use different detection
thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters from the
mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and middle columns
of Figure \ref{fig_detFalsRateNFW} show the detection rates for halos in the
(mass, redshift) planes with detection thresholds set to $1.5\sigma$ and
$3.0\sigma$ of the noise peaks' distributions, respectively.  The right column
of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
detections per square degree as functions of detection thresholds. The first,
second, and third rows of Figure \ref{fig_detFalsRateNFW} correspond to the
$lambda=3.5,4.0,5.0$, respectively.

>>>>

The right panel of Figure \ref{fig_detoffsets} shows the average redshift of
true detections for each halo. The estimated redshifts are lower than the true
redshifts by about $0.03$ for halos in the low-redshift range ($z\leq 0.4$).
For halos at $0.4<z\leq 0.85$, the relative redshift bias is below $0.5\%$. The
standard deviation of the redshift estimation is $0.092$.

With the intent to suppress false detections, we select peaks with values
greater than an ad-hoc threshold as candidates of galaxy clusters following
\citet{WL-massMap-clusDet-HSC-Miyazaki2018}.  The threshold is set to a few
times the standard deviation of the noise peaks. We use different detection
thresholds ($1.5\sigma$ and $3.0\sigma$) to detect galaxy clusters from the
mass maps reconstructed with $\lambda=3.5,4.0,5.0$. The left and middle columns
of Figure \ref{fig_detFalsRateNFW} show the detection rates for halos in the
redshift-mass planes with detection thresholds set to $1.5\sigma$ and
$3.0\sigma$ of the noise peaks' distributions, respectively.  The right column
of Figure \ref{fig_detFalsRateNFW} shows the corresponding numbers of false
detections per square degree as functions of detection thresholds.
